Verifying Demonstrations

### 2017-08-18 conclusions.tex
Adds open problems to conclusions

@@

\begin{frame}<presentation>
  \begin{remark}
    \begin{itemize}
      \item All current methods lack most of verifiability.
      \item Some provide universal verifiability (V\ref{UniversalVerif}).

@@

>>>>

\subsection<presentation>{Related work}

@@

\begin{frame}<presentation>
  \begin{remark}
    \begin{itemize}
      \item All current methods lack most of verifiability.
      \item Some provide universal verifiability.

@@

\subsection{Open problems}

\begin{frame}
  \begin{question}
    \begin{itemize}
      \item How to avoid Sybil?
      \item Government can sign as many certificates as they like using their 
        national ID systems.
      \item Tie to something unique: phone, phone subscription?
      \item Register twice?
    \end{itemize}
  \end{question}

  \begin{question}
    Can we piggyback on existing \acp{PKI}?
    E.g.~\cite{Cinderella}.
  \end{question}

  \begin{question}
    This is similar to the double-spending problem for cryptocurrencies, can 
    we reuse any such techniques?
    (Not like in Bitcoin, but more like ecash~\cite{ecash} and the like.)
  \end{question}
\end{frame}

\begin{frame}
\begin{question}
  How can we do \acp{LP} with 1000s of witnesses each?
  Can we do some preprocessing?
  Ad-hoc networks, broadcast \acp{LP}?
\end{question}
\end{frame}

\begin{frame}
\begin{question}
  Why should anyone trust these witnesses?
  What are the assumptions?
  Signed over a short period of time?\footnote{%
    In a sense, if they collude they have shown support for the cause.
    As long as they are not Sybil it should be fine?
  }
\end{question}

\begin{question}
  What if Alice acts as a witness for Eve's agents?
  Can that violate her privacy?
\end{question}

\begin{question}
  What if Eve's agents act as witnesses?
  Can they track their signatures to track users?
  Can Alice detect if this happens?
\end{question}
\end{frame}

\begin{frame}
  \begin{question}
    Malicious nodes want to provide Alice with a view that her proof is 
    included.
    Everyone else is provided a view without Alice.
    How can we ensure a consistent view for everyone?
    (Probably similar to the solution in Joakim's thesis.)
  \end{question}

  \begin{question}
    Under the protest conditions, we might have natural network splits.
    Is this a useful scenario?
  \end{question}

  \begin{question}
    How can we do blockchain branch and merge?
    That is needed to recover from the above attack.
  \end{question}
\end{frame}

\begin{frame}
  \begin{question}
    Shall we offer a platform that is run by a variety of institutions who 
    offers to verify protests?
    Or go strictly peer-to-peer?
  \end{question}
  \begin{question}
    If strictly peer-to-peer, and only run by protesters, one can infer that 
    they are protesters by running such a node.
    Can this be mitigated?
  \end{question}
\end{frame}

\begin{frame}
  \begin{question}
    How do we submit the proofs to storage?
    Voting normally uses mix-nets.
    Submit over Tor~\cite{Tor}?
  \end{question}

  \mode<presentation>{
  \begin{remark}
    Without anonymous submission we don't get vote privacy, thus no receipt 
    freeness either.
  \end{remark}
  }
\end{frame}
